A Lightweight, Swappable Voxel Ray-Tracer

### 2025-04-18 paper/paper.tex
Wrote Camera section (#36)

[Elaborate on camera and ray instantiation]

>>>>

Any image of the scene must be viewed from somewhere and at some angle; this is handled by the \texttt{Camera} controller.
The \texttt{Camera} holds several attributes corresponding to the camera's position, orientation, field of view, and related values.
From these, other values such as the distance in the scene between each pixel, the location of the top-left pixel in the scene, and the boundaries of the visible area are also calculated.
The \texttt{Camera} class contains a \texttt{get\_ray} function that receives pixel coordinates and creates a \texttt{Ray} object from the camera's position into a direction corresponding to these coordinates.

In further detail, when creating a Camera object, there are seven parameters the user may specify; otherwise, default values are used. They are as follows:
\begin{itemize}
  \item \texttt{img\_width}: The width of the image in pixels.
  \item \texttt{img\_height}: The height of the image in pixels.
  \item \texttt{vertical\_fov}: The vertical field of view in degrees.
  \item \texttt{lookfrom}: The 3D coordinates of the camera.
  \item \texttt{lookat}: The 3D coordinates of the point the camera is pointed towards.
  \item \texttt{cam\_up}: A vector representing the "up" direction relative to the scene.
  \item \texttt{focus\_dist}: Distance from the camera to the focus point.
\end{itemize}

From these, the program then converts the \texttt{vertical\_fov} from degrees to radians, then calculates the height angle \texttt{h}, multiplying it by \texttt{2 * focus\_dist} to get the \texttt{viewport\_height}.
Then, it uses the ratio of the image dimensions, \texttt{img\_width} and \texttt{img\_height}, to calculate the \texttt{viewport\_width}.

It also creates an orthonormal basis for the camera through a series of cross products: 
\begin{itemize} 
  \item First, the forwards-vector (z-axis), \texttt{w} is calculated by normalizing a vector from \texttt{lookfrom} to \texttt{lookto}.
  \item Then, the right-vector (x-axis), \texttt{u} is calculated by taking the cross-product between \texttt{w} and \texttt{cam\_up} and normalizing.
  \item Finally, the up-vector (y-axis), \texttt{v} is calculated by taking the cross-product between \texttt{u} and \texttt{w}.
\end{itemize}
\begin{figure}[htbp]
  \centerline{\includegraphics[width=\linewidth]{orthonormal-basis}}
  \caption{The orthonormal basis after each step.}
  \label{orthonormal-basis}
\end{figure}

The vectors \texttt{viewport\_u} and \texttt{viewport\_v} are then calculated by multiplying \texttt{u} by \texttt{viewport\_width} and \texttt{v} by \texttt{viewport\_height}, respectively.
Dividing them by the image dimensions, we get \texttt{pixel\_delta\_u} and \texttt{pixel\_delta\_v}, representing the horizontal and vertical distances between each pixel.
Then, we subtract half of the \texttt{viewport\_width} and \texttt{viewport\_height} from the center and add half of \texttt{pixel\_delta\_u} and \texttt{pixel\_delta\_v} to get the scene location of the top-left pixel, \texttt{pixel00\_loc}.

These calculated values are then used in the \texttt{get\_ray} function as follows:
The function takes in the pixel coordinates, \texttt{i} and \texttt{j}; it calculates \texttt{pixel\_sample} by starting from the top-left pixel \texttt{pixel00\_loc} and adding \texttt{i * pixel\_delta\_u} and \texttt{j * pixel\_delta\_v} to it.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=\linewidth]{pixel-delta-grid}}
  \caption{The \texttt{get\_ray} function, visualized. In a 4x4 pixel image, this ray goes through the pixel in the second row, second column.}
  \label{pixel-delta-grid}
\end{figure}

Then, it returns a \texttt{Ray} object with origin in \texttt{center} and direction going from there into \texttt{pixel\_sample}.
